\plaintitle

### 2016-05-19 chi/papers/2017/referrals/referrals.tex
major revisions to intro and generally framing need to update the rest of the paper to reflect the change in topics/categories that we look through

\section{Introduction}
This section should outline the trend of contemporary gig work in the last 10 years,
in particular tracking the changes since
\citeauthor{crowdworkFuture} discussed
\citetitle{crowdworkFuture}
in \citeyear{crowdworkFuture}
\cite{crowdworkFuture}.
This would review the literature since then,
then point to the movements toward worker unionization, advocacy, etc\dots
that have happened in the last year or two.

@@

\subsection{Piecework as a lens to understand gig work}
It's not new that researchers have discussed gig work as an extension or resurgence
of piecework, but it is sufficiently important for the framing of this argument that
it merits a more direct treatment and some explanation here.
\citeauthor{crowdworkFuture}
investigate the future of crowd work by
situating and interrogating it through ``piecework'',
a term almost lost to history, but which for a time described
work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration})
\cite{crowdworkFuture}.
This work was largely in textiles and was predominantly done by women,
which by itself is a topic worthy of unpacking
\cite{scott1975women}.
Given the scope, however,
we will have to leave this complex topic with the superficial takeaway that
piecework and microtasks share some structural similarities:
\begin{inlinelist}
\item the work is done in the home;
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy.
\end{inlinelist}

@@

This paper will argue that the similarity is more than striking;
it was an inevitable milestone in the maturation of the type of work that is reemerging today.
\textit{How to continue???}

>>>>

\section{Introduction}
In the past decade
microtasks, the ``sharing economy'', and other instantiations of on--demand contract labor
have grown in popularity both in the academic community as well as the collective consciousness
\cite{Ross,CrowdsourcingUserStudies,uberAlgorithm}.

This section should outline the trend of contemporary gig work in the last 10 years,
in particular tracking the changes since
\citeauthor{crowdworkFuture} discussed
\citetitle{crowdworkFuture}
in \citeyear{crowdworkFuture}
\cite{crowdworkFuture}.
This would review the literature since then,
then point to the movements toward worker unionization, advocacy, etc\dots
that have happened in the last year or two.

@@

\subsection{Piecework as a lens to understand gig work}
It's not new to discuss gig work as an extension or even a resurgence of piecework
\cite{crowdworkFuture,fixingChaos}.
Nevertheless, it's important enough for the framing of this argument that
a more direct treatment and some explanation is worthwhile.
\citeauthor{crowdworkFuture}
investigate the future of crowd work by
situating and interrogating it through ``piecework'',
a term almost lost to history, but which for a time described
work done in the home,
in manageable tasks,
often involving clear instructions
and payment only for work completed, not work done
(the differentiation, here, being that
one would be paid for the \textit{output} of the work,
not the \textit{duration})
\cite{crowdworkFuture}.
This work was largely in textiles and was predominantly done by women,
which by itself is a topic worthy of unpacking
\cite{scott1975women}.
Given the scope, however,
we will have to leave this complex topic with the superficial takeaway that
piecework and microtasks share some structural similarities:
\begin{inlinelist}
\item the work is done in the home;
\item the worker is paid for each discrete piece of work done, regardless of time or effort; and
\item the worker's status
(not only socially, but also economically)
is ambiguous, or at least the subject of some controversy.
\end{inlinelist}

@@

This paper will argue that the similarity is more than striking;
it was an inevitable milestone in the maturation of the type of work that is reemerging today.
``But'',
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor there is nothing new under the sun''
\cite{scholz2012digital}.
Indeed, we will attempt to reason about more than the larger--scale progression from
the discretization of work toward scientific management and future steps;
we will attempt to make sense of how the modern processes in digital labor,
in particular the use of the Internet as a medium to manage as well as \textit{do} work,
affect these unfolding events.
